---
title: "College Search"
author: "PhiPrime"
fontsize: 11pt
output: 
        pdf_document:
                toc: true
                toc_depth: 3
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# College Selection  
The colleges that we will be evaluating are loaded into an object in the following code block. They are entered in with respect to their size in decending order. They were manually selected from **[a search](https://www.collegedata.com/en/explore-colleges/college-search/SearchByPreference/?SearchByPreference.SearchType=0&SearchByPreference.CollegeName=&SearchByPreference.City=&SearchByPreference.States=CA&SearchByPreference.States=CO&SearchByPreference.States=CT&SearchByPreference.States=DC&SearchByPreference.States=FL&SearchByPreference.States=MD&SearchByPreference.States=MA&SearchByPreference.States=NY&SearchByPreference.States=NC&SearchByPreference.States=OR&SearchByPreference.States=PA&SearchByPreference.States=RI&SearchByPreference.States=VT&SearchByPreference.States=VA&SearchByPreference.States=WA&SearchByPreference.States=WV&SearchByPreference.StudentBodySizes=&SearchByPreference.PublicPrivate=&SearchByPreference.GenderMixes=C&SearchByPreference.EntranceDifficulties=5&SearchByPreference.FreshmanSatisfaction=&SearchByPreference.GraduationRate=&SearchByPreference.CostOfAttendance=&SearchByPreference.FinancialNeedMet=&SearchByPreference.StudentDebt=&SearchByPreference.IncludeStudentsWithNeed=false&SearchByPreference.MeritAid=&SearchByPreference.IncludeClubSports=false&SearchByPreference.WomensSports=&SearchByPreference.MensSports=&SearchByPreference.BackgroundNative=&SearchByPreference.BackgroundAfricanAmerican=&SearchByPreference.BackgroundAsian=&SearchByPreference.BackgroundHispanic=&SearchByPreference.BackgroundInternational=&SearchByPreference.DisciplineIncludeAll=false&SearchByPreference.AcademicDisciplines=27.03&SearchByPreference.AcademicDisciplines=27.01&SearchByPreference.AcademicDisciplines=27.05#)** with the following queries:  
+ **State**: CA, CO, CT, DC, FL, MD, MA, NY, NC, OR, PA, RI, VT, VA, WA, WV  
+ **Gender Mix**: Coed  
+ **Entrance Difficulty**: Most Difficult  
+ **Academic Major**: Applied Mathematics, Mathematics, Statistics  
```{r}
colleges <- c("University of California Berkeley",
              "Cornell University",
              "University of Pennsylvania",
              "Stanford University",
              "Carnegie Mellon University",
              "Brown University",
              "Duke University",
              "Yale University",
              "Johns Hopkins University",
              "Lehigh University",
              "Bucknell University",
              "Gettysburg College",
              "Pomona College",
              "Swarthmore College",
              "Haverford College")
urlExt <- gsub(" ", "-", colleges)
```


# Load Data  
```{r message = FALSE}
#Loading packages
library(tidyverse)
library(httr)
library(XML)
library(data.table)
```

All pages about colleges on *collegedata.com* have a standard base url with an extention that is the respective college's name.  
```{r}
baseUrl <- "https://www.collegedata.com/college/"
urls <- sapply(urlExt, function(x){paste0(baseUrl, x)})
#Simplify names
names(urls) <- c("Berkeley", "Cornell", "PA Uni", "Stanford", 
                 "Carnegie Mellon", "Brown", "Duke", "Yale", "JHU",
                 "Lehigh", "Bucknell", "Gettysburg", "Pomona", 
                 "Swarthmore", "Haverford")
```


```{r}
getCollegeData <- function(baseurl){

d <- data.frame(profile = "", numStudents = NaN, percentMale = NaN, 
                adminRate = "", adminDeadline = "", avgGPA = NaN,
                cost = NaN, avgClassSize = NaN, campusPopulation = NaN,
                nearestMetropolitan = "", percentOnCampusHousing = NaN,
                mascot = "", percentInFraternities = NaN, percentWhite = NaN,
                city = "", zip = "", state = "", phone = "", email = "",
                appFee = NaN, transferAdmission = "", summerCourses = NA,
                popularDisciplines = "", 
                fullFacultyCount = NaN, partFacultyCount = NaN, 
                studentCount = NaN, percentPhD = NaN,
                tutoring = NA, masters = "", doctoral = "", colors = "",
                avgAge = NaN, campusSize = "")

#Overview
content <- content(GET(baseurl, as = "text"))
parsed <- htmlParse(content, asText = TRUE)

d$profile <- gsub("\n", "", xpathSApply(parsed, "//p", xmlValue)[64])
d$numStudents <- as.numeric(gsub(",","",xpathSApply(
        parsed, "//span[1]", xmlValue)[37]))
d$percentMale <- as.numeric(gsub("[)(%]", "", 
                           xpathSApply(parsed, "//b", xmlValue)[2])
                      )/100
d$adminRate <- xpathSApply(parsed, "//dd[2]", xmlValue)[1]
d$adminDeadline <- xpathSApply(parsed, "//dd[5]", xmlValue)[1]
d$avgGPA <- as.numeric(xpathSApply(parsed, "//dd[1]", xmlValue)[2])
d$cost <- as.numeric(gsub("[$,]", "", xpathSApply(
        parsed, "//dd[1]", xmlValue)[3]))

getAvgClassSize <- function(parsedHtml) {
        classData <- xpathSApply(parsedHtml, "//dd[4]", xmlValue)[4]
        classData <- strsplit((strsplit(classData, "% of classes")[[1]][1:6]
                  #Disregard over 100 because I likely won't
                  #Encounter them as a transfer student
                  ), " students: ")
        freqs <- as.numeric(sapply(1:6, function(x){classData[[x]][2]}))/100
        groupedMeans <- c((2+10)/2, (10+20)/2, (20+30)/2, 
                          (30+40)/2, (40+50)/2, (50+100)/2)
        
        sum(freqs*groupedMeans)
}
d$avgClassSize <- getAvgClassSize(parsed)
d$campusPopulation <- as.numeric(gsub(",", "", 
                             xpathSApply(parsed, "//dd[1]", xmlValue)[5]))
d$nearestMetropolitan <- xpathSApply(parsed, "//dd[2]", xmlValue)[5]
d$percentOnCampusHousing <- as.numeric(gsub(" ", "", strsplit(
        xpathSApply(parsed, "//dd[4]", xmlValue)[5],
                               "%")[[1]][1]))/100
d$mascot <- xpathSApply(parsed, "//dd[6]", xmlValue)[2]
d$percentInFraternities <- as.numeric(gsub(" ", "", strsplit(
        xpathSApply(parsed, "//dd[8]", xmlValue),
                               "%")[[1]][1]))/100
d$percentWhite <- as.numeric(gsub("%(.*)", "", gsub("(.*)slander", "", 
                 xpathSApply(parsed, "//dd[1]", xmlValue)[6])))/100

#Admission
admissionTab <- "/?tab=profile-admission-tab"
content <- content(GET(paste0(baseurl, admissionTab), as = "text"))
parsed <- htmlParse(content, asText = TRUE)

d$address <- xpathSApply(parsed, "//dd[1]", xmlValue)[2]
csz <- strsplit(xpathSApply(parsed, "//dd[2]", xmlValue)[2], ",")
d$city <- csz[[1]][1]

sz <- strsplit(csz[[1]][2], " ")
d$state <- sz[[1]][2]
d$zip <- sz[[1]][3]

d$phone <- xpathSApply(parsed, "//dd[3]", xmlValue)[1]
d$email <- gsub("\n", "", xpathSApply(parsed, "//dd[5]", xmlValue)[1])
d$appFee <- xpathSApply(parsed, "//dd[2]", xmlValue)[3]
d$transferAdmission <- (xpathSApply(parsed, "//dd[8]", 
                        xmlValue)[1] == "Transfer applications accepted")

#Money Matters
moneyTab <- "/?tab=profile-money-tab"
#No additional content of interest
#content <- content(GET(paste0(baseurl, moneyTab), as = "text"))
#parsed <- htmlParse(content, asText = TRUE)

#Academics
academicsTab <- "/?tab=profile-academics-tab"
content <- content(GET(paste0(baseurl, academicsTab), as = "text"))
parsed <- htmlParse(content, asText = TRUE)

d$summerCourses <- (xpathSApply(parsed, "//dd[2]", xmlValue)[1] == 
                               "Offered")
d$popularDisciplines <- xpathSApply(parsed, "//dd[1]", xmlValue)[2]
d$fullFacultyCount <- as.numeric(xpathSApply(parsed, "//dd[1]", xmlValue)[4])
d$partFacultyCount <- as.numeric(xpathSApply(parsed, "//dd[2]", xmlValue)[4])
d$percentPhD <- as.numeric(gsub("%", "",
                        xpathSApply(parsed, "//dd[3]", xmlValue)[4]))/100
d$tutoring <- (xpathSApply(parsed, "//dd[2]", xmlValue)[7] == "Available")
d$masters <- xpathSApply(parsed, "//p[1]", xmlValue)[37]
d$doctoral <- xpathSApply(parsed, "//p[2]", xmlValue)[16]

#Campus Life
campusTab <- "/?tab=profile-campus-tab"
content <- content(GET(paste0(baseurl, campusTab), as = "text"))
parsed <- htmlParse(content, asText = TRUE)

d$campusSize <- xpathSApply(parsed, "//dd[3]", xmlValue)[1]
d$colors <- xpathSApply(parsed, "//dd[3]", xmlValue)[6]


#Students
studentsTab <- "/?tab=profile-students-tab"
content <- content(GET(paste0(baseurl, studentsTab), as = "text"))
parsed <- htmlParse(content, asText = TRUE)

d$studentCount <- as.numeric(gsub(",", "", 
                          xpathSApply(parsed, "//dd[2]", xmlValue)[1]))
d$avgAge <- as.numeric(xpathSApply(parsed, "//dd[8]", xmlValue)[1])
return(d)
}
```
```{r warnings = FALSE}
collegesData <- rbindlist(lapply(urls, getCollegeData))
collegesData <- cbind(colleges, collegesData)
```

# Plots  


# Consider Weights  


# Results  

